---
title: "ESM206-assignment4"
author: "Claire Madden, Bridget Gibbons, Andrew Paterson"
date: "11/12/2018"
output: word_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}

library(tidyverse)
library(vcdExtra)
library(RColorBrewer)
library(dplyr)
library(car)
library(effsize)
library(kableExtra)
library(ggrepel)

```

```{r, echo=FALSE, message=FALSE}

lobster_size <- read_csv("lobster_size_abundance.csv")
lobster_traps <- read_csv("lobster_traps.csv")

```


```{r, echo=FALSE}

lobster_size2 <- as.data.frame(lobster_size)
lobster_size_tidy <- expand.dft(lobster_size2, freq = "COUNT")

#If you guys don't want to change the site name here, no problem!
size_tidy <- lobster_size_tidy %>% 
  mutate(Site=
    case_when(
      SITE == "NAPL" ~ "Naples Reef",
      SITE == "AQUE" ~ "Arroyo Quemado",
      SITE == "MOHK" ~ "Mohawk Reef",
      SITE == "IVEE" ~ "Isla Vista",
      SITE == "CARP" ~ "Carpinteria"
    )
  ) %>% 
  select(-SITE)

traps_tidy <- lobster_traps %>% 
    mutate(Site=
    case_when(
      SITE == "NAPL" ~ "Naples Reef",
      SITE == "AQUE" ~ "Arroyo Quemado",
      SITE == "MOHK" ~ "Mohawk Reef",
      SITE == "IVEE" ~ "Isla Vista",
      SITE == "CARP" ~ "Carpinteria"
    )
  ) %>% 
  select(-SITE)


```

#Part 1
```{r, echo=FALSE}

abundance_summary <- lobster_size %>%
  group_by(SITE, YEAR) %>% 
  summarize(
    count = sum(COUNT))


traps_simple <- lobster_traps %>% 
  filter(SITE == "AQUE" | SITE == "NAPL" | SITE == "MOHK" | SITE == "IVEE" | SITE == "CARP")

traps_summary <- traps_simple %>% 
  group_by(SITE, YEAR) %>% 
  summarize(
    traps = sum(TRAPS))


```



```{r, echo = FALSE, include = FALSE}

abundance_traps <- full_join(abundance_summary, traps_summary) %>% 
      mutate(Site=
    case_when(
      SITE == "NAPL" ~ "Naples Reef",
      SITE == "AQUE" ~ "Arroyo Quemado",
      SITE == "MOHK" ~ "Mohawk Reef",
      SITE == "IVEE" ~ "Isla Vista",
      SITE == "CARP" ~ "Carpinteria"))



traps_scatter <- ggplot(abundance_traps, aes(x = YEAR, y = traps))+
  geom_point(aes(color = Site))+
  geom_line(aes(color = Site))+
  theme_classic()+
  labs(x = "Year", y= "Number of Traps")
traps_scatter




```

**Figure 1: Fishing Pressure at Five Locations in the Santa Barbara Channel (2012-2017)** Total annual number of commercial lobster trap bouys counted at Arroyo Quemado, Carpinteria, Isla Vista, Mohawk, and Naples reefs.  Data collected in lobster fishing season (October through March) every two to four weeks. Data used with permission of Santa Barbara Coastal Long Term Ecological Research Project $^1$.



```{r, echo = FALSE}
count_scatter <- ggplot(abundance_traps, aes(x = YEAR, y = count))+
  geom_point(aes(color = Site))+
  geom_line(aes(color = Site))+
  theme_classic()+
  labs(x = "Year", y = "Lobsters Counted")

count_scatter
```





```{r, echo=FALSE}
#Display Graphs

traps_scatter


```
**Figure 1: Fishing Pressure at Five Locations in the Santa Barbara Channel (2012-2017)** Total annual number of commercial lobster trap bouys counted at Arroyo Quemado, Carpinteria, Isla Vista, Mohawk, and Naples reefs. Lobster trap bouy counts at Isla Vista and Naples marine protected areas are both zero across between 2012 - 2017. Data collected in lobster fishing season (October through March) every two to four weeks. Data used with permission of Santa Barbara Coastal Long Term Ecological Research Project $^4$.

```{r, echo = FALSE}

count_scatter

```
**Figure 2: Fishing Pressure at Five Locations in the Santa Barbara Channel (2012-2017)** Total annual number of lobsters counted at Arroyo Quemado, Carpinteria, Isla Vista, Mohawk, and Naples reefs.  Data collected in lobster fishing season (October through March) every two to four weeks. Data used with permission of Santa Barbara Coastal Long Term Ecological Research Project $^4$.


#Part 2 (Andrew)

```{r, echo=FALSE, include= FALSE}

#Filter for just 2017 results for Part 2, and Exploratory Histogram and QQ Plots

size_2017 <- size_tidy %>% 
  filter(YEAR == "2017") %>%
  select(SIZE, Site)

carapace_hist <- ggplot(size_2017, aes(x = SIZE))+
  geom_histogram(bins = 23, aes(fill = Site))+
  facet_wrap(~Site)

carapace_hist

carapace_qq <- ggplot(size_2017, aes(sample = SIZE))+
  geom_qq()+
  facet_wrap(~Site)

carapace_qq

#The data looks roughly normally distributed, and all sites have a sample size of greater than 30. 

```

```{r echo=FALSE, message=FALSE, include=FALSE}

#Levene's Test for Equal Variances, since we have more than two groups
#H0: Variances are equal
#HA: Variances are not equal

carapace_levene <- leveneTest(SIZE ~ Site, data = size_2017)
carapace_levene

#We reject the null hypothesis of equal variances (p < .001) based on Levene's Test.  However, we can examine the variances of each site to see if the largest is less than four times the smallest variance.  

carapace_variances <- size_2017 %>% 
  group_by(Site) %>% 
  summarize(
    Variance = var(SIZE)
  )

carapace_variances

#The largest variance is well less than four times the smallest variance, so we can assume accept the null hypothesis of equal variances and run an ANOVA.

#H0: Mean carapace sizes are equal at all sites
#HA: Mean carapace sizes vary for lobsters from at least two sites.

carapace_aov <- aov(SIZE ~ Site, data = size_2017)
summary(carapace_aov)

#boxplot for sizes in case we want to include this
size_2017_boxplot <- ggplot(size_2017, aes(x = Site, y = SIZE))+
  geom_boxplot()+
  scale_x_discrete()+
  ylab("Carapace Size (mm)")+
  xlab("Site")+
  theme_classic()+
  geom_jitter(width = .2, alpha = .4, aes(color = Site))+
  theme(legend.position = "none")
##Improve color scheme here?

#Making a summary table and column graph for lobster sizes

size_summary <- size_2017 %>% 
  group_by(Site) %>%
  summarize(
    'Median' = round(median(SIZE), 2),
    'Maximum' = round(max(SIZE), 2),
    'Mean' = round(mean(SIZE), 2),
    'Standard_Deviation' = round(sd(SIZE), 2),
    'Sample_Size' = length(SIZE)
  )

size_2017_col <- ggplot(size_summary, aes(x = Site, y = Mean))+
  geom_col(fill = "indianred2")+
  geom_errorbar(aes(ymin=Mean-Standard_Deviation, ymax=Mean+Standard_Deviation), size = .3, width = .2)+
  theme_classic()+
  labs(x = "Site", y = "Carapace Size (mm)")+
  scale_y_continuous(breaks=seq(0,100, by = 20), expand = c(0,0), limits = c(0,100))

#With p = .0085, we reject the null, and assume mean carapace length varies between lobsters from at least two sites. At least two populations were taken from populations with different means.

#Post-hoc testing using Tukey's HSD

carapace_ph <- TukeyHSD(carapace_aov)
carapace_ph

#Lobster sizes differed significantly only between Naples Reef and Carpenteria, and Naples Reef and Isla Vista. 

#Cohen's d

naples_2017 <- size_2017 %>% 
  filter(Site == "Naples Reef")

carp_2017 <- size_2017 %>% 
  filter(Site == "Carpinteria")

iv_2017 <- size_2017 %>% 
  filter(Site == "Isla Vista")

nap_carp_effsize <- cohen.d(naples_2017$SIZE, carp_2017$SIZE)
nap_carp_effsize

nap_iv_effsize <- cohen.d(naples_2017$SIZE, iv_2017$SIZE)
nap_iv_effsize

#Small effect size between both locations

```


**Figure 3: Mean Lobster Carapace Length at Five LTER Sites in the Santa Barbara Channel in 2017**  Mean lobster carapace length (mm) measured at five locations: Arroyo Quemado, Carpinteria, Isla Vista, Mohawk Reef, and Naples Reef, all Long-Term Ecological Research sites.  Mean carapace length only differed significantly between Naples Reef and Isla Vista, and between Naples Reef and Carpinteria; all other pairwise comparisons yielded no significant difference (IN-LINE REFERENCING) (one-way ANOVA, F(X) = X, p = x), with post-hoc Tukey’s HSD (alpha = 0.05). 

```{r, echo=FALSE, message=FALSE, include=FALSE}

#Comparing the lobster sizes across the sites, and putting this information in a table.

size_summary <- size_2017 %>% 
  group_by(Site) %>% 
  summarize("Mean Size" = round(mean(SIZE), 2),
            "Standard Deviation" = round(sd(SIZE), 2),
            "Sample Size" = length(Site))

size_summary

size_final <- kable(size_summary, col.names = c("Site", "Mean Carapace Size", "Standard Deviation", "Sample Size"), align = "c") %>% 
  kable_styling(bootstrap_options = c("striped"))
  
size_final

```

```{r, echo=FALSE}

size_final

```

```{r, echo=FALSE}


size_2017_boxplot

```

**Figure 4: Mean Lobster Carapace Length at five LTER sites in the Santa Barbara Channel in 2017** Mean lobster carapace length (mm) measured at five locations: Arroyo Quemado, Carpinteria, Isla Vista, Mohawk Reef, and Naples Reef.  Boxes indicate the 25th and 75th percentiles of observations, lower and upper boundaries respectively, and the dark center line indicates the median at each location. Whiskers, or the vertical lines, indicate observations within 1.5 times the interquartile range indicated by the box.  Solitary points indicate measurements outside of the interquartile whisker range. Colored jitter points indicate individual lobster size measurements.

#Part 3 (Bridget)

#The following chunks are comparing 2012 and 2017 for each site individually 

```{r, echo=FALSE}
#MPA Sites data frames

mpa_size_2012 <- lobster_size_tidy %>% 
  filter(SITE == "IVEE" | SITE == "NAPL", YEAR == "2012") %>% 
  select(YEAR, SITE, SIZE)

mpa_size_2017 <- lobster_size_tidy %>% 
  filter(SITE == "IVEE" | SITE == "NAPL", YEAR == "2017") %>% 
  select(YEAR, SITE, SIZE)

```

```{r, echo=FALSE, include=FALSE}
#MPA Sites exploratory histograms and qq plots

mpa_2012_hist <- ggplot(mpa_size_2012, aes(x = SIZE)) + 
  geom_histogram(bins = 8) +
  facet_wrap(~ SITE)

mpa_2012_hist

mpa_2012_qq <- ggplot(mpa_size_2012, aes(sample = SIZE)) +
  geom_qq() +
  facet_wrap(~ SITE)

mpa_2012_qq

mpa_2017_hist <- ggplot(mpa_size_2017, aes(x = SIZE)) + 
  geom_histogram(bins = 8) +
  facet_wrap(~ SITE)

mpa_2017_hist

mpa_2017_qq <- ggplot(mpa_size_2017, aes(sample = SIZE)) +
  geom_qq() +
  facet_wrap(~ SITE)

mpa_2017_qq
```

```{r, echo=FALSE}
#NonMPA sites data frames

nonmpa_size_2012 <- lobster_size_tidy %>% 
  filter(SITE == "AQUE" | SITE == "MOHK" | SITE == "CARP", YEAR == "2012") %>% 
  select(YEAR, SITE, SIZE)

nonmpa_size_2017 <- lobster_size_tidy %>% 
  filter(SITE == "AQUE" | SITE == "MOHK" | SITE == "CARP", YEAR == "2017") %>% 
  select(YEAR, SITE, SIZE)
```

```{r, echo=FALSE, include=FALSE}
#NonMPA Sites exploratory histograms and qq plots

nonmpa_2012_hist <- ggplot(nonmpa_size_2012, aes(x = SIZE)) + 
  geom_histogram(bins = 8) +
  facet_wrap(~ SITE)

nonmpa_2012_hist

nonmpa_2012_qq <- ggplot(nonmpa_size_2012, aes(sample = SIZE)) +
  geom_qq() +
  facet_wrap(~ SITE)

nonmpa_2012_qq

nonmpa_2017_hist <- ggplot(nonmpa_size_2017, aes(x = SIZE)) + 
  geom_histogram(bins = 8) +
  facet_wrap(~ SITE)

nonmpa_2017_hist

nonmpa_2017_qq <- ggplot(nonmpa_size_2017, aes(sample = SIZE)) +
  geom_qq() +
  facet_wrap(~ SITE)

nonmpa_2017_qq
```

```{r, echo=FALSE, include=FALSE}
#Site 1: Arroyo Quemado - nonMPA
#Make vectors for the 2012 and 2017 values
 
aq_2012 <- nonmpa_size_2012 %>% 
 filter(SITE == "AQUE") %>% 
 pull(SIZE)
 
aq_2017 <- nonmpa_size_2017 %>% 
 filter(SITE == "AQUE") %>% 
 pull(SIZE)
 
#Run an F-test for equal variance
#H0: ratio of variances = 1
#HA: ratio of variances NOT = 1
 
aq_ftest <- var.test(aq_2012, aq_2017)
aq_ftest
 
#Retain null, variances are equal. Run student's t-test
 
aq_ttest <- t.test(aq_2012, aq_2017, var.equal = TRUE)
aq_ttest
 
#p-valye of 0.2097, no significant difference in lobster sizes
 
#calculate effect size
 
aq_effsize <- cohen.d(aq_2012, aq_2017)
aq_effsize

#effect size is small (-0.256)

```


```{r, echo=FALSE, include=FALSE}
#Site 2: Carpinteria - nonMPA
#Make vectors for the 2012 and 2017 values
 
carp_2012 <- nonmpa_size_2012 %>% 
 filter(SITE == "CARP") %>% 
 pull(SIZE)
 
carp_2017 <- nonmpa_size_2017 %>% 
 filter(SITE == "CARP") %>% 
 pull(SIZE)

#Run an F-test for equal variance
#H0: ratio of variances = 1
#HA: ratio of variances NOT = 1
 
carp_ftest <- var.test(carp_2012, carp_2017)
carp_ftest
 
#Retain null, variances are equal. Run student's t-test
 
carp_ttest <- t.test(carp_2012, carp_2017, var.equal = TRUE)
carp_ttest
 
#p-valye of 0.1819, no significant difference in lobster sizes
 
#calculate effect size
 
carp_effsize <- cohen.d(carp_2012, carp_2017)
carp_effsize
 
#effect size is negligible (-0.159)
```


```{r, echo=FALSE, include=FALSE}
#Site 3: Mohawk Reef - nonMPA

#Make vectors for the 2012 and 2017 values

mohk_2012 <- nonmpa_size_2012 %>% 
 filter(SITE == "MOHK") %>% 
 pull(SIZE)
 
mohk_2017 <- nonmpa_size_2017 %>% 
 filter(SITE == "MOHK") %>% 
 pull(SIZE)

#Run an F-test for equal variance
#H0: ratio of variances = 1
#HA: ratio of variances NOT = 1
 
mohk_ftest <- var.test(mohk_2012, mohk_2017)
mohk_ftest
 
#Retain null, variances are equal. Run student's t-test
 
mohk_ttest <- t.test(mohk_2012, mohk_2017, var.equal = TRUE)
mohk_ttest
 
#p-valye < 0.001, significant difference in lobster sizes
 
#calculate effect size
 
mohk_effsize <- cohen.d(mohk_2012, mohk_2017)
mohk_effsize
 
#effect size is medium (0.54)
```


```{r, echo=FALSE, include=FALSE}

#Site 4: Isla Vista - MPA

#Make vectors for the 2012 and 2017 values

iv_2012 <- mpa_size_2012 %>% 
  filter(SITE == "IVEE") %>% 
  pull(SIZE)

iv_2017 <- mpa_size_2017 %>% 
  filter(SITE == "IVEE") %>% 
  pull(SIZE)

#Run an F-test for equal variance
#H0: ratio of variances = 1
#HA: ratio of variances NOT = 1

iv_ftest <- var.test(iv_2012, iv_2017)
iv_ftest

#Retain null, variances are equal. Run student's t-test

iv_ttest <- t.test(iv_2012, iv_2017, var.equal = TRUE)
iv_ttest

#p-valye of 0.0599, no significant difference in lobster sizes

#calculate effect size

iv_effsize <- cohen.d(iv_2012, iv_2017)
iv_effsize

#effect size is small (-0.377)

```


```{r, echo=FALSE, include=FALSE}

#Site 5: Naples Reef - MPA

#Make vectors for the 2012 and 2017 values

napl_2012 <- mpa_size_2012 %>% 
  filter(SITE == "NAPL") %>% 
  pull(SIZE)

napl_2017 <- mpa_size_2017 %>% 
  filter(SITE == "NAPL") %>% 
  pull(SIZE)

#Run an F-test for equal variance
#H0: ratio of variances = 1
#HA: ratio of variances NOT = 1

napl_ftest <- var.test(napl_2012, napl_2017)
napl_ftest

#Retain null, variances are equal. Run student's t-test

napl_ttest <- t.test(napl_2012, napl_2017, var.equal = TRUE)
napl_ttest

#p-valye of 0.5002, no significant difference in lobster sizes

#calculate effect size

napl_effsize <- cohen.d(napl_2012, napl_2017)
napl_effsize

#effect size is small (-0.283)
```

**Figures 4-5: Lobster Carapace Sizes at sites inside Marine Protected Areas (2012 and 2017)** Lobster carapace (mm) data collected at two Long-Term Ecological Research sites within Marine Protected Areas in the Santa Barbara Channel: Isla Vista (n=26 in 2012, n=606 in 2017) and Naples Reef (n=6 in 2012, n=112 in 2017). Mean lobster size only differed significantly between 2012 and 2017 at Isla Vista; pairwise comparison at Naples Reef yielded no significant difference (IN LINE REFERENCING).

```{r, echo=FALSE}

#Make boxplots for MPA sites

#Isla Vista

iv_box <- lobster_size_tidy %>% 
  filter(SITE == "IVEE", YEAR == "2012" | YEAR == "2017") %>% 
  select(YEAR, SIZE) %>% 
  mutate(YEAR = factor(YEAR)) %>% 
  group_by(YEAR)

iv_boxplot <- ggplot(iv_box, aes(x = YEAR, y = SIZE)) +
  geom_boxplot()+
  theme_classic()+
  geom_jitter(width = 0.2, alpha = 0.4, aes(color = YEAR))+
  scale_y_continuous(breaks = seq(0, 160, by = 20), limits = c(0,160))+
  labs(x = "Year", y = "Carapace Size (mm)", title = "Figure 4: Isla Vista")+
  theme(legend.position = "none")

iv_boxplot

#Naples

napl_box <- lobster_size_tidy %>% 
  filter(SITE == "NAPL", YEAR == "2012" | YEAR == "2017") %>% 
  select(YEAR, SIZE) %>% 
  mutate(YEAR = factor(YEAR)) %>% 
  group_by(YEAR)

napl_boxplot <- ggplot(napl_box, aes(x = YEAR, y = SIZE)) +
  geom_boxplot()+
  theme_classic()+
  geom_jitter(width = 0.2, alpha = 0.4, aes(color = YEAR))+
  scale_y_continuous(breaks = seq(0, 160, by = 20), limits = c(0,160))+
  labs(x = "Year", y = "Carapace Size (mm)", title = "Figure 5: Naples Reef")+
  theme(legend.position = "none")

napl_boxplot

 #theme_classic()+
  #geom_jitter(width = .2, alpha = .4, aes(color = Site))+
  #theme(legend.position = "none")

```

**Figures 6-8: Lobster Carapace Sizes at sites outside of Marine Protected Areas in 2012 and 2017** Lobster carapace (mm) data collected at three Long-Term Ecological Research sites outside of Marine Protected Areas in the Santa Barbara Channel: Arroyo Quemado, (n = 38 in 2012, n = 68 in 2017), Carpinteria (n = 78 in 2012, n = 705 in 2017), and Mohawk Reef (n = 83 in 2012, n = 178 in 2017). Mean lobster size only differed significantly between 2012 and 2017 at Mohawk Reef; pairwise comparison at all other sites yielded no significant difference (IN LINE REFERENCING). ADD CORRESPONDING NUMBERS TO EACH GRAPH TITLE.

```{r, echo=FALSE}
#Make boxplots for Non-MPA sites

#Arroyo Quemado

aq_box <- lobster_size_tidy %>% 
  filter(SITE == "AQUE", YEAR == "2012" | YEAR == "2017") %>% 
  select(YEAR, SIZE) %>% 
  mutate(YEAR = factor(YEAR)) %>% 
  group_by(YEAR)

aq_boxplot <- ggplot(aq_box, aes(x = YEAR, y = SIZE)) +
  geom_boxplot()+
  theme_classic()+
  geom_jitter(width = 0.2, alpha = 0.4, aes(color = YEAR))+
  scale_y_continuous(breaks = seq(0, 160, by = 20), limits = c(0,160))+
  labs(x = "Year", y = "Carapace Size (mm)", title = "Figure 6: Arroyo Quemado")+
  theme(legend.position = "none")

aq_boxplot

#Carpinteria

carp_box <- lobster_size_tidy %>% 
  filter(SITE == "CARP", YEAR == "2012" | YEAR == "2017") %>% 
  select(YEAR, SIZE) %>% 
  mutate(YEAR = factor(YEAR)) %>% 
  group_by(YEAR)

carp_boxplot <- ggplot(carp_box, aes(x = YEAR, y = SIZE)) +
  geom_boxplot()+
  theme_classic()+
  geom_jitter(width = 0.2, alpha = 0.4, aes(color = YEAR))+
  scale_y_continuous(breaks = seq(0, 160, by = 20), limits = c(0,160))+
  labs(x = "Year", y = "Carapace Size (mm)", title = "Figure 7: Carpinteria")+
  theme(legend.position = "none")

carp_boxplot

#Mohawk Reef

mohk_box <- lobster_size_tidy %>% 
  filter(SITE == "MOHK", YEAR == "2012" | YEAR == "2017") %>% 
  select(YEAR, SIZE) %>% 
  mutate(YEAR = factor(YEAR)) %>% 
  group_by(YEAR)

mohk_boxplot <- ggplot(mohk_box, aes(x = YEAR, y = SIZE)) +
  geom_boxplot()+
  theme_classic()+
  geom_jitter(width = 0.2, alpha = 0.4, aes(color = YEAR))+
  scale_y_continuous(breaks = seq(0, 160, by = 20), limits = c(0,160))+
  labs(x = "Year", y = "Carapace Size (mm)", title = "Figure 8: Mohawk Reef")+
  theme(legend.position = "none")

mohk_boxplot

```


```{r}
#Statistics for table

#Isla Vista

iv_mean_2012 <- mean(iv_2012)
iv_sd_2012 <- sd(iv_2012)
iv_mean_2017 <- mean(iv_2017)
iv_sd_2017 <- sd(iv_2017)
iv_mean_diff <- iv_mean_2017 - iv_mean_2012

#Naples

napl_mean_2012 <- mean(napl_2012)
napl_sd_2012 <- sd(napl_2012)
napl_mean_2017 <- mean(napl_2017)
napl_sd_2017 <- sd(napl_2017)
napl_mean_diff <- napl_mean_2017 - napl_mean_2012

#Carpenteria

carp_mean_2012 <- mean(carp_2012)
carp_sd_2012 <- sd(carp_2012)
carp_mean_2017 <- mean(carp_2017)
carp_sd_2017 <- sd(carp_2017)
carp_mean_diff <- carp_mean_2017 - carp_mean_2012

#Mohawk

mohk_mean_2012 <- mean(mohk_2012)
mohk_sd_2012 <- sd(mohk_2012)
mohk_mean_2017 <- mean(mohk_2017)
mohk_sd_2017 <- sd(mohk_2017)
mohk_mean_diff <- mohk_mean_2017 - mohk_mean_2012

#Aque

aq_mean_2012 <- mean(aq_2012)
aq_sd_2012 <- sd(aq_2012)
aq_mean_2017 <- mean(aq_2017)
aq_sd_2017 <- sd(aq_2017)
aq_mean_diff <- aq_mean_2017 - aq_mean_2012


```


#Part 4

```{r, echo=FALSE, message=FALSE}
#Make table with counts of legal and illegal lobsters for each site

legal_sizes <- lobster_size_tidy %>% 
  filter(SITE == "IVEE" | SITE == "NAPL" | SITE == "MOHK" | SITE == "AQUE" | SITE == "CARP") %>% 
  filter(YEAR == 2017) %>% 
  filter(SIZE != "-99999") %>% 
  select(YEAR, SITE, SIZE) %>% 
  mutate(legality = ifelse(SIZE > 83, "legal", "illegal")) %>% 
  count(SITE, legality) %>% 
  spread(legality, n) %>% 
  select(-SITE)

rownames(legal_sizes) <- c("AQUE", "CARP", "IVEE", "MOHK", "NAPL")
  
```

```{r, echo=FALSE, include=FALSE}
#Make table with proportions

legal_prop <- prop.table(as.matrix(legal_sizes), 1)

legal_prop
```

```{r, echo=FALSE, include=FALSE}
#Run chi square test on the legalilty table (original data, not prop table)

legal_x2 <- chisq.test(legal_sizes) 
legal_x2

#There is a significant association between site location and the amount of legal/illegal lobsters

```



References:
1. Reed, D. . 2017. SBC LTER: Reef: Abundance, size and fishing effort for California Spiny Lobster (Panulirus interruptus), ongoing since 2012. Santa Barbara Coastal Long Term Ecological Research Project. doi:10.6073/pasta/81ce20b29614ec99d85d54907eaa3e8e

